Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

1.Males are less likely to support Biden than Females,
2.Women most likely to vote for Biden,
3.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

>>>>

1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
2.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
